---
title: "Sandbox study Simon"
author: "Kristian Tempelmans Plat & Simon Brett"
date: "5 March 2018"
output: html_document
---

# Setup (suppressed)
```{r setup, echo=FALSE,message=FALSE}

setwd("C:/Users/ct886924/Documents/STUDIES/Study1_MT/Simon_data/Full_dataset")
simondata=read.csv("Full_simondata_set.csv")

# Spreadsheet was too long for actual data
simondata = na.omit(simondata)

# get mean AQ based on all trials to use for AQ.mc later
AQ_means = mean(simondata$AQ)


# Libraries
library(lme4)
library(lmerTest)
library(simr)

```

# LMM before outlier removal

Conclusion: no effects whatsoever

``` {r beforeoutlierremoval}

simondata_before_removal = simondata

model_before=lmer(Bias~FB..1..vs.MC.2.*ConRew
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|ConRew)
            +(1+FB..1..vs.MC.2.|Participant),simondata_before_removal,REML=FALSE)

summary(model_before)

     # Conclusion: no effects whatsoever
```

----------------------------------------------------------------------

# Outlier removal for FB and MC separately

This approach excludes identified as outliers (M +- 3 SD ) within condition (FB / MC)

?? FB trials are removed this way

??MC trials are removed this way

?? / ??? trials = ? %

Note that more FB trials are removed than MC trials.

As outliers are all(?) in the expected direction (but just extreme), we are at risk at handicapping ourselves.


``` {r outliers}

m_bias_FB = mean(simondata$Bias[simondata$FBMem == "FB"])
sd_bias_FB = sd(simondata$Bias[simondata$FBMem == "FB"])

hi_FB = m_bias_FB + 3 * sd_bias_FB
lo_FB = m_bias_FB - 3 * sd_bias_FB

m_bias_Mem = mean(simondata$Bias[simondata$FBMem == "Mem"])
sd_bias_Mem = sd(simondata$Bias[simondata$FBMem == "Mem"])

hi_Mem = m_bias_Mem + 3 * sd_bias_Mem
lo_Mem = m_bias_Mem - 3 * sd_bias_Mem



simondata_FB = simondata[simondata$FBMem == "FB",]
simondata_Mem = simondata[simondata$FBMem == "Mem",]

simondata_FB_removed = simondata_FB[simondata_FB$Bias > hi_FB,]
simondata_FB = simondata_FB[simondata_FB$Bias < hi_FB,]
simondata_Mem_removed = simondata_Mem[simondata_Mem$Bias > hi_Mem,]
simondata_Mem = simondata_Mem[simondata_Mem$Bias < hi_Mem,]

# See which trials/scenarios are most frequently outliers
sort(simondata_FB_removed$TrialNumber)
sort(simondata_Mem_removed$TrialNumber)

simondata_new = rbind(simondata_FB,simondata_Mem)
simondata = simondata_new

# Note: participant 34 had 5 / 16 outliers!

```


# Participant outliers

Note: Current outlier approach could be changed to SDpooled approach later

``` {r participantoutliers,echo=FALSE}

simondata_backup = simondata


Means_participants = ddply(simondata, c("Participant", "FB..1..vs.MC.2."), summarise, meanBias = mean(Bias))

Participants_FB = Means_participants[Means_participants$FB..1..vs.MC.2. == 1,]
Participants_MC = Means_participants[Means_participants$FB..1..vs.MC.2. == 2,]

Participants_FB$isoutlier = rep(NA,length(Participants_FB$Participant))

m_P_FB = mean(Participants_FB$meanBias)
sd_P_FB = sd(Participants_FB$meanBias)

hi_P_FB = m_P_FB + 3* sd_P_FB
lo_P_FB = m_P_FB - 3* sd_P_FB

for (i in 1:length(Participants_FB$meanBias)){
  if (Participants_FB$meanBias[i] < hi_P_FB & Participants_FB$meanBias[i] > lo_P_FB){
    Participants_FB$isoutlier[i] = 0
  } else {
    Participants_FB$isoutlier[i] = 1
  }
}


m_P_MC = mean(Participants_MC$meanBias)
sd_P_MC = sd(Participants_MC$meanBias)

hi_P_MC = m_P_MC + 3* sd_P_MC
lo_P_MC = m_P_MC - 3* sd_P_MC

for (i in 1:length(Participants_MC$meanBias)){
  if (Participants_MC$meanBias[i] < hi_P_MC & Participants_MC$meanBias[i] > lo_P_MC){
    Participants_MC$isoutlier[i] = 0
  } else {
    Participants_MC$isoutlier[i] = 1
  }
}

# Remove outlier participant
simondata = simondata[simondata$Participant != 1,]

# Switch to dataset including participant outliers (currently not active)
# simondata = simondata_backup

```










# Linear mixed models

After outlier removal:

Main effect of condition

Main effect of reward

``` {r linearmixedmodels}


# Model 1: same as Simon's model 3 but WITH interaction
#   includes
# - main effects of Condition and Reward
# - interaction between Condition and Reward
# - control variables Age and Gender
# - random effect for Condition|Participant

model1=lmer(Bias~FB..1..vs.MC.2.*ConRew
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|Participant),simondata,REML=FALSE)

summary(model1)

    # Model 1 conclusion:
      # Condition = Sig; FB > MC [bias]
      # Reward    = Sig; Pos > Neg
      # Con*Rew   = Sig; Bias is higher for Negative



# With outliers

model1_o=lmer(Bias~FB..1..vs.MC.2.*ConRew
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|Participant),simondata_before_removal,REML=FALSE)

summary(model1_o)



# Model 2 [EXACTLY THE SAME AS SIMON'S MODEL 3]
#   includes
# - main effects of Condition and Reward
# - interaction between Condition and Reward
# - control variables Age and Gender
# - random effect for Condition|Participant
# - random effect for Condition|Reward (but should this not be taken away, as Reward is a within-subject variable?)
    # - random effects based on Simon's Model1

model2=lmer(Bias~FB..1..vs.MC.2.*ConRew
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|ConRew)
            +(1+FB..1..vs.MC.2.|Participant),simondata,REML=FALSE)

summary(model2)


model2_o=lmer(Bias~FB..1..vs.MC.2.*ConRew
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|ConRew)
            +(1+FB..1..vs.MC.2.|Participant),simondata_before_removal,REML=FALSE)

summary(model2_o)

# Model 3 [Simon's model 3 but with random effects from model 2]

model3 = lmer(Bias~ConRew*FB..1..vs.MC.2.+Age+Gender+(
  1+ConRew|Participant) + (1+ConRew|FB..1..vs.MC.2.),simondata,REML = FALSE)

summary(model3)

model3_O = lmer(Bias~ConRew*FB..1..vs.MC.2.+Age+Gender+(
  1+ConRew|Participant) + (1+ConRew|FB..1..vs.MC.2.),simondata_before_removal,REML = FALSE)

summary(model3_O)


```


Conclusion for models 1-3:
   
  Condition = Sig; FB > MC [bias]
    
  Reward    = Sig; Pos > Neg
    
  Con*Rew   = Sig; Bias is higher for Negative

Model 3: Also marginally significant effect of age



# Linear mixed models with AQ

``` {r withaq}

# AQ mean-centred


for (i in 1:length(simondata$AQ)){
  simondata$AQ.mc[i] = simondata$AQ[i] - AQ_means
}

for (i in 1:length(simondata_before_removal$AQ)){
  simondata_before_removal$AQ.mc[i] = simondata_before_removal$AQ[i] - AQ_means
}


# Model 4: with AQ, 1 random effect
model4=lmer(Bias~FB..1..vs.MC.2.*ConRew*AQ.mc
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|Participant),simondata,REML=FALSE)

summary(model4)

model4_o=lmer(Bias~FB..1..vs.MC.2.*ConRew*AQ.mc
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|Participant),simondata_before_removal,REML=FALSE)

summary(model4_o)

# Model 5: with AQ, 2 random effects
model5=lmer(Bias~FB..1..vs.MC.2.*ConRew*AQ.mc
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|Participant)
            +(1+ConRew|Participant),simondata,REML=FALSE)

summary(model5)

model5_o=lmer(Bias~FB..1..vs.MC.2.*ConRew*AQ.mc
            +Age
            +Gender
            +(1+FB..1..vs.MC.2.|Participant)
            +(1+ConRew|Participant),simondata_before_removal,REML=FALSE)

summary(model5_o)


```

AQ only visible in marginally significant interaction with Reward

# Linear mixed model with four-way interaction (Con,Rew,AQ,TrialNo)

``` {r fourway}


# Model 6: four-way interaction of (Rew,Con,AQ,TrialNo)
model6=lmer(Bias~FB..1..vs.MC.2.*ConRew*TrialNumber*AQ +FB..1..vs.MC.2. +ConRew
            +Age+Gender
            +(1+FB..1..vs.MC.2.|Participant),simondata,REML=FALSE)

summary(model6)


model6_o=lmer(Bias~FB..1..vs.MC.2.*ConRew*TrialNumber*AQ +FB..1..vs.MC.2. +ConRew
            +Age+Gender
            +(1+FB..1..vs.MC.2.|Participant),simondata_before_removal,REML=FALSE)

summary(model6_o)



```



# Linear models

``` {r linearmodels}

simple.model1 = lm(Bias~FB..1..vs.MC.2.*ConRew,simondata)
summary(simple.model1)

simple.model1_o = lm(Bias~FB..1..vs.MC.2.*ConRew,simondata_before_removal)
summary(simple.model1_o)

simple.model2 = lm(Bias~FB..1..vs.MC.2.*ConRew + Age + Gender,simondata)
summary(simple.model2)

simple.model2_o = lm(Bias~FB..1..vs.MC.2.*ConRew + Age + Gender,simondata_before_removal)
summary(simple.model2_o)

simple.model3 = lm(Bias~FB..1..vs.MC.2.*ConRew*AQ.mc + Age + Gender,simondata)
summary(simple.model3)

simple.model3_o = lm(Bias~FB..1..vs.MC.2.*ConRew*AQ.mc + Age + Gender,simondata_before_removal)
summary(simple.model3_o)


```

In simple model 1: significant main effects and interaction

In simple model 2: significant main effects and interaction AND effect of Age

In simple model 3 (with AQ included): same as above, plus marg sig Condition*AQ 


# Visualisation (work in progress)
``` {r visualisation}

library(ggplot2)

# faulty
p <- ggplot(simondata, aes(x=FB..1..vs.MC.2., y=Bias, colour=ConRew)) +
  geom_line(aes(y=predict(model4), group=Participant, size="Subjects")) +
  geom_line(data=simondata, aes(y=predict(model4, level=0, newdata=simondata), size="Population")) +
  scale_size_manual(name="Predictions", values=c("Subjects"=0.5, "Population"=3)) +
  theme_bw(base_size=22) 
print(p)

```
