---
title: "Sandbox study - multiple approaches"
author: "Kristian Tempelmans Plat & Simon Brett"
date: "15 March 2018"
output: html_document
runtime: shiny
---

# Sandbox study: the effect of reward on false belief bias

This script looks at Simon Brett's Sandbox task data from various angles.

Per approach, the following analyses are done:

* linear mixed model
* linear model
* visualisation


In addition, this script investigates whether prosopagnosia traits explains task performance

1. Do those participants who fail the memory task have a higher prosopagnosia score?

2. In the dataset with passing participants, is there a correlation between prosopagnosia and FB bias?







``` {r librarypreparation, echo = FALSE, message = FALSE, warning = FALSE}

library(lme4)
library(lmerTest)
library(simr)
library(plyr)

library(sjPlot)
library(sjmisc)
library(ggplot2)
library(plyr)

theme_set(theme_sjplot())


```


``` {r prep_1_2, echo = FALSE, warning = FALSE, message = FALSE}

# --------
# Option 1
# --------

# FULL

    # Get dataset
setwd("C:/Users/ct886924/Documents/STUDIES/Study1_MT/Simon_data/Full_dataset")
Full=read.csv("Full_simondata_set.csv")

    # Remove NAs (if they are present)
Full = na.omit(Full)

    # Mean AQ
Full.AQ_means = mean(Full$AQ)
for (i in 1:length(Full$AQ)){
  Full$AQ.mc[i] = Full$AQ[i] - Full.AQ_means
}

    # Rename columns
names(Full)[14] = "FBvMC"
names(Full)[15] = "SvL"

####################################################################################################


# PASS

    # Get dataset
setwd("C:/Users/ct886924/Documents/STUDIES/Study1_MT/Simon_data")
Pass=read.csv("MergedRdata2.csv")

    # Mean AQ
Pass.AQ_means = mean(Pass$AQ)
for (i in 1:length(Pass$AQ)){
  Pass$AQ.mc[i] = Pass$AQ[i] - Pass.AQ_means
}

    # Rename columns
names(Pass)[14] = "FBvMC"
names(Pass)[15] = "SvL"


####################################################################################################

# --------
# Option 2
# --------


# FULL_ALL

    # No split

Full_All = Full

####################################################################################################

# FULL_SEP

    # Split dataset into False Belief and Memory Control subset

Full_FB = Full[Full$FBvMC == 1,]
Full_MC = Full[Full$FBvMC == 2,]


####################################################################################################


# PASS_ALL

    # No split

Pass_All = Pass

####################################################################################################


# PASS_SEP

    # Split dataset into False Belief and Memory Control subset

Pass_FB = Pass[Pass$FBvMC == 1,]
Pass_MC = Pass[Pass$FBvMC == 2,]


####################################################################################################


```


``` {r normcheck, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}

library(nortest)


    # Normality check for dataset
ad.test(Full_All$Bias)
ad.test(Pass_All$Bias)

```

``` {r pre_3_and_4, echo = FALSE, warning = FALSE, message = FALSE}
# ------------
# Option 3 & 4
# ------------


# FULL_ALL_3SD_TP ####

    # Removal of outlier trials

m.Full_All = mean(Full_All$Bias)
sd.Full_All = sd(Full_All$Bias)

hi.Full_All.3SD = m.Full_All + 3 * sd.Full_All
lo.Full_All.3SD = m.Full_All - 3 * sd.Full_All

Full_All_3SD_T = Full_All[Full_All$Bias < hi.Full_All.3SD,]
Full_All_3SD_T = Full_All_3SD_T[Full_All_3SD_T$Bias > lo.Full_All.3SD,]


    # Removal of outlier participants

Full_All_3SD_T.participants = ddply(Full_All_3SD_T, c("Participant", "FBvMC"), summarise, meanBias = mean(Bias))

Full_All_3SD_T.participants$isoutlier = rep(NA,length(Full_All_3SD_T.participants$Participant))

m.Full_All_3SD_T.participants = mean(Full_All_3SD_T.participants$meanBias)
sd.Full_All_3SD_T.participants = sd(Full_All_3SD_T.participants$meanBias)

hi.Full_All_3SD_T.participants = m.Full_All_3SD_T.participants + 3 * sd.Full_All_3SD_T.participants
lo.Full_All_3SD_T.participants = m.Full_All_3SD_T.participants - 3 * sd.Full_All_3SD_T.participants

for (i in 1:length(Full_All_3SD_T.participants$meanBias)){
  if (Full_All_3SD_T.participants$meanBias[i] < hi.Full_All_3SD_T.participants & Full_All_3SD_T.participants$meanBias[i] > lo.Full_All_3SD_T.participants){
    Full_All_3SD_T.participants$isoutlier[i] = 0
  } else {
    Full_All_3SD_T.participants$isoutlier[i] = 1
  }
}

    # Dataset specification
Full_All_3SD_TP = Full_All_3SD_T[Full_All_3SD_T$Participant != 1,]


####################################################################################################

# FULL_ALL_2SD_TP ####

    # 2 SD cutoff because normality assumption is violated for Full_All data set

hi.Full_All.2SD = m.Full_All + 2 * sd.Full_All
lo.Full_All.2SD = m.Full_All - 2 * sd.Full_All

Full_All_2SD_T = Full_All[Full_All$Bias < hi.Full_All.2SD,]
Full_All_2SD_T = Full_All_2SD_T[Full_All_2SD_T$Bias > lo.Full_All.2SD,]


    

####################################################################################################

# FULL_ALL_PSD_TP ####

####################################################################################################


# FULL_ALL_3SD_PT ####

####################################################################################################

# FULL_ALL_2SD_PT ####

# 2 SD cutoff because normality assumption is violated for Full_All data set

####################################################################################################

# FULL_ALL_PSD_PT ####

####################################################################################################



# FULL_SEP_3SD_TP ####

####################################################################################################

# FULL_SEP_2SD_TP ####


####################################################################################################

# FULL_SEP_PSD_TP ####

####################################################################################################


# FULL_SEP_3SD_PT ####

####################################################################################################

# FULL_SEP_2SD_PT ####

####################################################################################################

# FULL_SEP_PSD_PT ####

####################################################################################################




# PASS_ALL_3SD_TP ####

####################################################################################################

# PASS_ALL_2SD_TP ####


# 2 SD cutoff because normality assumption is violated for Pass_All data set

    # Removal of outlier trials

m.Pass_All = mean(Pass_All$Bias)
sd.Pass_All = sd(Pass_All$Bias)

hi.Pass_All.2SD = m.Pass_All + 2 * sd.Pass_All
lo.Pass_All.2SD = m.Pass_All - 2 * sd.Pass_All

Pass_All_2SD_T = Pass_All[Pass_All$Bias < hi.Pass_All.2SD,]
Pass_All_2SD_T = Pass_All_2SD_T[Pass_All_2SD_T$Bias > lo.Pass_All.2SD,]


    # Removal of outlier participants

Pass_All_2SD_T.participants = ddply(Pass_All_2SD_T, c("Participant", "FBvMC"), summarise, meanBias = mean(Bias))

Pass_All_2SD_T.participants$isoutlier = rep(NA,length(Pass_All_2SD_T.participants$Participant))

m.Pass_All_2SD_T.participants = mean(Pass_All_2SD_T.participants$meanBias)
sd.Pass_All_2SD_T.participants = sd(Pass_All_2SD_T.participants$meanBias)

hi.Pass_All_2SD_T.participants = m.Pass_All_2SD_T.participants + 2 * sd.Pass_All_2SD_T.participants
lo.Pass_All_2SD_T.participants = m.Pass_All_2SD_T.participants - 2 * sd.Pass_All_2SD_T.participants

for (i in 1:length(Pass_All_2SD_T.participants$meanBias)){
  if (Pass_All_2SD_T.participants$meanBias[i] < hi.Pass_All_2SD_T.participants & Pass_All_2SD_T.participants$meanBias[i] > lo.Pass_All_2SD_T.participants){
    Pass_All_2SD_T.participants$isoutlier[i] = 0
  } else {
    Pass_All_2SD_T.participants$isoutlier[i] = 1
  }
}

    # Dataset specification
Pass_All_2SD_TP = Pass_All_2SD_T[Pass_All_2SD_T$Participant != 1,]




####################################################################################################

# PASS_ALL_PSD_TP ####

####################################################################################################


# PASS_ALL_3SD_PT ####

####################################################################################################

# PASS_ALL_2SD_PT ####

# 2 SD cutoff because normality assumption is violated for Pass_All data set

####################################################################################################

# PASS_ALL_PSD_PT ####

####################################################################################################



# PASS_SEP_3SD_TP ####

####################################################################################################

# PASS_SEP_2SD_TP ####

####################################################################################################

# PASS_SEP_PSD_TP ####

####################################################################################################


# PASS_SEP_3SD_PT ####

####################################################################################################

# PASS_SEP_2SD_PT ####

####################################################################################################

# PASS_SEP_PSD_PT ####

####################################################################################################




```


``` {r Full_All_3SD_TP, echo = FALSE, eval = FALSE}

# Linear mixed model
Full_All_3SD_TP.lmm = lmer(Bias~FBvMC*ConRew
            +Age
            +Gender
            +(1+FBvMC|Participant),Full_All_3SD_TP,REML=FALSE)

summary(Full_All_3SD_TP.lmm)

# Linear model

Full_All_3SD_TP.lm1 = lm(Bias~FBvMC*ConRew + Age + Gender,Full_All_3SD_TP)
summary(Full_All_3SD_TP.lm1)

Full_All_3SD_TP.lm2 = lm(Bias~FBvMC*ConRew*AQ.mc + Age + Gender,Full_All_3SD_TP)
summary(Full_All_3SD_TP.lm2)


# Visualisation

plot_model(Full_All_3SD_TP.lm2, type = "pred", terms = c("FBvMC", "AQ.mc [-20,0,20]", "ConRew"))


```

``` {r Pass_All_2SD_TP, echo = FALSE, eval = FALSE}

# Linear mixed model
Pass_All_2SD_TP.lmm = lmer(Bias~FBvMC*ConRew
            +Age
            +Gender
            +(1+FBvMC|Participant),Pass_All_2SD_TP,REML=FALSE)

summary(Pass_All_2SD_TP.lmm)

# Linear model

Pass_All_2SD_TP.lm1 = lm(Bias~FBvMC*ConRew + Age + Gender,Pass_All_2SD_TP)
summary(Pass_All_2SD_TP.lm1)

Pass_All_2SD_TP.lm2 = lm(Bias~FBvMC*ConRew*AQ.mc + Age + Gender,Pass_All_2SD_TP)
summary(Pass_All_2SD_TP.lm2)


# Visualisation
plot_model(Pass_All_2SD_TP.lm1, type = "pred", terms = c("FBvMC"))

plot_model(Pass_All_2SD_TP.lm1, type = "pred", terms = c("FBvMC", "ConRew"))

plot_model(Pass_All_2SD_TP.lm2, type = "pred", terms = c("FBvMC", "AQ.mc [-10,0,10]", "ConRew"))
plot_model(Pass_All_2SD_TP.lm2, type = "pred", terms = c("AQ.mc","FBvMC", "ConRew"))



# With Condition and Reward as factors
Pass_All_2SD_TP.fac = Pass_All_2SD_TP

Pass_All_2SD_TP.fac$ConRew = as.factor(Pass_All_2SD_TP.fac$ConRew)
Pass_All_2SD_TP.fac$FBvMC = as.factor(Pass_All_2SD_TP.fac$FBvMC)

Pass_All_2SD_TP.fac.lm1 = lm(Bias~FBvMC*ConRew + Age + Gender,Pass_All_2SD_TP.fac)
summary(Pass_All_2SD_TP.fac.lm1)

Pass_All_2SD_TP.fac.lm2 = lm(Bias~FBvMC*ConRew*AQ.mc + Age + Gender,Pass_All_2SD_TP.fac)
summary(Pass_All_2SD_TP.fac.lm2)


plot_model(Pass_All_2SD_TP.fac.lm1, type = "pred", terms = c("FBvMC"))
plot_model(Pass_All_2SD_TP.fac.lm1, type = "pred", terms = c("FBvMC", "ConRew"))
plot_model(Pass_All_2SD_TP.fac.lm2, type = "pred", terms = c("FBvMC", "AQ.mc [-10,0,10]", "ConRew"))

sd(Pass_All_2SD_TP.fac$AQ.mc)
plot_model(Pass_All_2SD_TP.fac.lm2, type = "pred", terms = c("FBvMC", "AQ.mc [-6.77,0,6.77]", "ConRew"))




```


### Main choice (to be removed)

```{r data, echo = FALSE}

selectInput("data", "",
 c("Full_All_3SD_TP", "Pass_All_2SD_TP")) 

selectInput("type", "",
 c("Numeric", "Factors")) 


```




### Please select your data set based on the following parameters



1. Memory task performance
  + All participants                                  [Full]
  + Participants who passed the memory task           [Pass]
  
  
```{r option1, echo = FALSE}

selectInput("option1", "",
 c("Full", "Pass")) 


```
  
2. Outliers based on...
  + Full dataset                                      [All]
  + False Belief and Memory Control separately        [Sep]
  
  
```{r option2, echo = FALSE}

selectInput("option2", "",
 c("All", "Sep")) 


```


3. Outlier cutoff score
  + 3 SD (standard approach)                          [3SD]
  + 2 SD (if normality assumption is violated)        [2SD]
  + Pooled SD                                         [pSD]
  
```{r option3, echo = FALSE}

selectInput("option3", "",
 c("3SD", "2SD", "pSD")) 


```  
  
4. Outlier removal order
  + Trials, then participants (Bhisma's suggestion)   [TP]
  + Participants, then trials                         [PT]
  
```{r option4, echo = FALSE}

selectInput("option4", "",
 c("TP", "PT")) 


```


5. Condition and Reward as
  + Numeric values                                    [nume]
  + Factors                                           [fact]


```{r option5, echo = FALSE}

selectInput("option5", "",
 c("nume", "fact")) 


```


## Create chunk that shows chosen data set, by pasting the variables defined above together

Note: delete following chunk after full tree is created

```{r showdataset, echo = FALSE}

renderText({

  opt1 <- input$option1
  opt2 <- input$option2
  opt3 <- input$option3
  opt4 <- input$option4
  opt5 <- input$option5
  
  paste(c(opt1,"_",opt2,"_",opt3,"_",opt4,".",opt5), collapse = "")
    
})

```


Note: potentially add option to choose order of Condition, Reward and AQ for plots (X, Y and Z)

# Model output and visualisation

Note: Visualisation based on full model (Rew x Con x AQ)



## Number of trials in dataset

Note: use renderTable or other render function

## Linear mixed model results

Note: use renderTable or other render function

## Linear model results

Note: use renderTable or other render function


## Main effect of Belief condition

``` {r plot1, echo = FALSE}


renderPlot({
   choice <- get(input$data)
   
   if (input$type == "Numeric"){
  choice$FBvMC = as.numeric(choice$FBvMC)
  choice$ConRew = as.numeric(choice$ConRew)
} else if (input$type == "Factors"){
  choice$FBvMC = as.factor(choice$FBvMC)
  choice$ConRew = as.factor(choice$ConRew)
}
   
   
 choice.model1 = lm(Bias~FBvMC*ConRew*AQ.mc + Age + Gender,choice)
 plot_model(choice.model1, title = "Predicted bias per Condition", axis.title = c("False Belief vs Memory Control", "Bias"),  type = "pred", terms = c("FBvMC"))
}) 

```

## Belief x Reward

``` {r plot2, echo = FALSE}
renderPlot({
 choice <- get(input$data)
 
 
    
   if (input$type == "Numeric"){
  choice$FBvMC = as.numeric(choice$FBvMC)
  choice$ConRew = as.numeric(choice$ConRew)
} else if (input$type == "Factors"){
  choice$FBvMC = as.factor(choice$FBvMC)
  choice$ConRew = as.factor(choice$ConRew)
}
   
 
 
 choice.model2 = lm(Bias~FBvMC*ConRew*AQ.mc + Age + Gender,choice)
 plot_model(choice.model2, title = "Predicted bias per Condition x Reward", axis.title = c("False Belief vs Memory Control", "Bias"), type = "pred", terms = c("FBvMC", "ConRew"))
}) 


```

## Belief x Reward x AQ

NOTE: values for AQ lines should be +1SD and -1SD based on chosen dataset

``` {r plot3, echo = FALSE}

renderPlot({
 choice <- get(input$data)
 
    
   if (input$type == "Numeric"){
  choice$FBvMC = as.numeric(choice$FBvMC)
  choice$ConRew = as.numeric(choice$ConRew)
} else if (input$type == "Factors"){
  choice$FBvMC = as.factor(choice$FBvMC)
  choice$ConRew = as.factor(choice$ConRew)
}
   
 
 
 choice.model3 = lm(Bias~FBvMC*ConRew*AQ.mc + Age + Gender,choice)
 plot_model(choice.model3, title = "Predicted bias per Condition x AQ category x Reward", axis.title = c("False Belief vs Memory Control", "Bias"), type = "pred", terms = c("FBvMC", "AQ.mc [-6.77, 0, 6.77]", "ConRew"))
}) 

```



``` {r prosopagnosia, echo = FALSE, message = FALSE}

# Note: change dataset names to new names

# PI20_pass = ddply(simondata, "Participant", summarise, PI20_score = mean(PI20))
# PI20_full = ddply(simondata_full,"Participant",summarise, PI20_score = mean(PI20))

```